\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
...

In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
\begin{equation}
  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
\end{equation}
where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
\begin{eqnarray}
    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\ 
    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
\end{eqnarray}

The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space. Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
%\begin{equation}
%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
%  \label{e:force_balance}
%\end{equation}

@@

In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (Eq.\ref{cvfe_pressure}) while saturation is represented in node centered CV basis (Eq.\ref{cvfe_saturation}) control volume basis functions respectevely:

\begin{equation}
 p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
\label{cvfe_pressure}
\end{equation}

\begin{equation}
 S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
\label{cvfe_saturation}
\end{equation}

where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else. The saturation equation is solved explicitly after solving for pressure at each time.

>>>>

\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
\begin{equation}
  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
\end{equation}
where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
\begin{eqnarray}
    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\ 
    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
\label{v_and_p}
\end{eqnarray}

\noindent The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space. Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
%\begin{equation}
%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
%  \label{e:force_balance}
%\end{equation}

@@

In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (see Eq.\ref{v_and_p}, also known as shape functions, $\underline{\bf v}$ and $\underline{\bf p}$) while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.

\begin{comment}
\begin{equation}
 p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
\label{cvfe_pressure}
\end{equation}

\begin{equation}
 S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
\label{cvfe_saturation}
\end{equation}
\end{comment}

%where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
